\documentclass[11pt]{article}

% --- Packages ---
\usepackage[usenames, dvipsnames]{color} % Cool colors
\usepackage{enumerate, amsmath, amsthm, amssymb, mathrsfs, algorithm, algpseudocode, fontawesome, pifont, subfig, fullpage, csquotes, dashrule, tikz, bbm, booktabs, bm, hyperref}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage[numbers]{natbib}
\usepackage[normalem]{ulem}

% --- Misc. ---
\hbadness=10000 % No "underfull hbox" messages.
\setlength{\parindent}{0pt} % Removes all indentation.

% -- Commands --
\input{commands}

\title{ICLR 2019 Notes \\ \Large{New Orleans, LA, USA}}
\author{David Abel\footnote{\durl{http://david-abel.github.io}} \\ \durl{david_abel@brown.edu}}
\date{May 2019}

\begin{document}
\maketitle
\tableofcontents
\newpage


This document contains notes I took during the events I managed to make it to at (my first) ICLR, in New Orleans, LA, USA. Please feel free to distribute it and shoot me an email at \durl{david_abel@brown.edu} if you find any typos or other items that need correcting. 


\section{Conference Highlights}

Sadly, I missed more talks than normal this conference (and had to fly out a bit early so I missed a good chunk of Thursday). Some highlights:
\begin{itemize}
    \item Lots of continued discussion following the recent wave of conversations around Rich Sutton's bitter lesson\footnote{\url{http://incompleteideas.net/IncIdeas/BitterLesson.html}}. The debate held at the main conference track (see Section~\ref{sec:debate}) and the panel at the SPiRL workshop\footnote{\url{http://spirl.info}} (see Section~\ref{sec:panel}) featured lots of insights about the topic -- highly recommended to check them out!
    \item The SPiRL workshop was {\it outstanding}. The speaker lineup, contributed talks, and panel were all exceptional (see Section~\ref{sec:spirl}). A huge thanks to the organizers for putting on such a great event.
    \item Hot topics: 1) Meta learning is very popular (particularly meta RL), and 2) Graph neural networks.
    \item Favorite talks: I loved the keynotes! I didn't make it to all of them but the ones I did catch were all fantastic. Definitely check out Prof. Zeynep Tufekci's amazing talk if you can find a video (my summary is in Section~\ref{sec:keynote_zeynep}). If I happen to find a recording I'll link it here.
    \item Some really nice papers in learning abstraction/hierarchies in RL: 1) ``Near-Optimal Representation Learning for Hierarchical Reinforcement Learning" by \citet{nachum2018near}, and 2) ``Learning Multi-Level Hierarchies with Hindsight" by \citet{levy2018learning}; and ``Learning Finite State Representations of Recurrent Policy Networks' by~\citet{koul2018learning}.
    \item A small thing, but I *loved* how large the poster were allowed to be (something like 5ft wide). Encouraged some great designs and easy viewing for the onlookers, even from a distance.
\end{itemize}

% ------------
% -- Sunday --
% ------------
\newpage
\section{Monday May 6th: Workshops}
\input{days/monday_5_6_19.tex}



% ------------
% -- Monday --
% ------------
\newpage
\section{Tuesday May 7th: Main Conference}
\input{days/tuesday_5_7_19.tex}



% ------------
% -- Tuesday --
% ------------
\newpage
\section{Wednesday May 8th: Main Conference}
\input{days/wednesday_5_8_19.tex}



% ---------------
% -- Wednesday --
% ---------------
\newpage
\section{Thursday May 9th: Main Conference}
\input{days/thursday_5_9_19.tex}





% --- Bibliography ---
\newpage
\bibliographystyle{plainnat}
\bibliography{iclr}

\end{document}